Dynamic capabilities and competitive advantage

### 2019-09-30 article4_tommylars.rnw
still struggling with framing

\Sexpr{resest[1,2]}
In a recent "state of the art" literature review on dynamic capabilities
\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
of strategic management" (p. 393). And indeed a considerable body of the extant literature
concerns itself with exactly this path to competitive advantage (refs from
shcilke). Still, a discourse regarding the contingencies of the dynamic
capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
will dynamic capabilities lead to competitive advantage?

>>>>

DC is often critizesd for being tautological and less focus has been placed on instances
when dynamism can lead to poorer competitive outcomes. 
Structural inertia, commitment \cite{schreyogg2007}. Under what conditions are changing
capabilities counterproducttive

The relationship between dynamic capabilities and competitive advantage has been one of
great contention in the extant literature \citep{Peteraf2013,Ambrosini2009}. From this
debate a richer understanding of how different dynamic capabilities (or functional forms
of them) work differently to change different types of firm resources
\citep{Helfat2015a,Teece2007,Ambrosini2009a} with implications for competitive advantage
\citep{Peteraf2013} has emerged. Increasingly the relationship between (1) dynamic
capabilities, (2) firm resources and routines, and competitive advantage is seen as a
complex system with interactions between different types of each 1 and 2. Many conceptual
contributions have excellently discussed varieties or functional forms of either dynamic
capabilities \citep{Ambrosini2009a,Helfat2015ad,DiStefano2014} or underlying resources or
routines \citep{Winter2003,Eisenhardt2000}. However, very few, is any, papers attempts to
integrate varieties at multiple levels simultaneously. The bulk of contributions focus
only on heterogeneity at the dynamic capabilities level, or at

work dDC offers a theory of how firms achieve
competitive advantage over time. Yet the DC theory suffers from contradictory claims about
competitive advantage as its outcome. On the one hand a stream of contributions argue that
DC will lead to competitive advantage because it operates by changing operational
capabilities in face of change and hence create strategic change (ref helfat). In this
view these changes result in complex and path dependent processes that will be
idiosyncratic to the firm and hard to imitate. Consequently, they can lead to competitive
advantage.

A contrary stream of literature argues that changes of operational capabilities over time
takes the form of routines and converges towards best practice (ref EM). Such best
practices are simpler and more observable routines that are both imitable and easy to
copy. Such firm resources are then not idiosyncratic and can consequently not be the
source of competitive advantage.

The way DC work differnelty throug changing two sets of operational capabilities = complex
and path dependent processes based capabilities, and simple rules/based routines.

These contradictory positions have been thoroughly discussed in earlier work (see
\cite{Peteraf2013} for a review). On the one hand DC takes the form of simple rules
shaping underlying routines. On the other hand they take the form of complex processes.

Regarding the action and the object ofthe action, simple rules are more likely to be
involved in developing something new in response to new opportunities, while complex
rou- tines are more concerned with changing existing resources and capabilities.

In a recent "state of the art" literature review on dynamic capabilities
\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
of strategic management" (p. 393). And indeed a considerable body of the extant literature
concerns itself with exactly this path to competitive advantage (refs from
shcilke). Still, a discourse regarding the contingencies of the dynamic
capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
will dynamic capabilities lead to competitive advantage?

### 2019-09-30 article4_tommylars.tex
still struggling with framing

\title{Dynamic capabilities and competitive advantag}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

0.343
In a recent "state of the art" literature review on dynamic capabilities
\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
of strategic management" (p. 393). And indeed a considerable body of the extant literature
concerns itself with exactly this path to competitive advantage (refs from
shcilke). Still, a discourse regarding the contingencies of the dynamic
capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
will dynamic capabilities lead to competitive advantage?

>>>>

\title{Dynamic capabilities and competitive advantage}
%\tnotetext[mytitlenote]{Fully documented templates are available in the elsarticle package on \href{http://www.ctan.org/tex-archive/macros/latex/contrib/elsarticle}{CTAN}.}

@@

The relationship between dynamic capabilities and competitive advantage has been one of
great contention in the extant literature \citep{Peteraf2013,Ambrosini2009}. From this
debate a richer understanding of how different dynamic capabilities (or functional forms
of them) work differently to change different types of firm resources
\citep{Helfat2015a,Teece2007,Ambrosini2009a} with implications for competitive advantage
\citep{Peteraf2013}.  has emerged.  work dDC offers a theory of how firms achieve
competitive advantage over time. Yet the DC theory suffers from contradictory claims about
competitive advantage as its outcome. On the one hand a stream of contributions argue that
DC will lead to competitive advantage because it operates by changing operational
capabilities in face of change and hence create strategic change (ref helfat). In this
view these changes result in complex and path dependent processes that will be
idiosyncratic to the firm and hard to imitate. Consequently, they can lead to competitive
advantage.

A contrary stream of literature argues that changes of operational capabilities over time
takes the form of routines and converges towards best practice (ref EM). Such best
practices are simpler and more observable routines that are both imitable and easy to
copy. Such firm resources are then not idiosyncratic and can consequently not be the
source of competitive advantage.

The way DC work differnelty throug changing two sets of operational capabilities = complex
and path dependent processes based capabilities, and simple rules/based routines.

These contradictory positions have been thoroughly discussed in earlier work (see
\cite{Peteraf2013} for a review). On the one hand DC takes the form of simple rules
shaping underlying routines. On the other hand they take the form of complex processes.

Regarding the action and the object ofthe action, simple rules are more likely to be
involved in developing something new in response to new opportunities, while complex
rou- tines are more concerned with changing existing resources and capabilities.

In a recent "state of the art" literature review on dynamic capabilities
\cite{Schilke2018} state that much of the attention and interest surrounding the theory is
that it offer a route to competitive advantage which they argue is "the virtual Holy Grail
of strategic management" (p. 393). And indeed a considerable body of the extant literature
concerns itself with exactly this path to competitive advantage (refs from
shcilke). Still, a discourse regarding the contingencies of the dynamic
capabilities-competitive advantage (DC-CA) nexus (?) has panned out in the literature,
most notably coined "the elephant in the room" \citep{Peteraf2013}: Under which conditions
will dynamic capabilities lead to competitive advantage?
